Cycles of the logistic map

### 2014-02-15 doc/pc.tex
Editing pc.tex

\documentclass[twocolumn]{revtex4-1}
%\usepackage[width=5.65in, height=9.3in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{centernot}
\usepackage{hyperref}
\usepackage{graphicx}
%\usepackage{times}
%\usepackage{setspace}
\usepackage{booktabs}
\usepackage{calc}
\usepackage{cancel} % strike out (cancel) in math mode
%\usepackage{appendix}
\begin{document}

@@

@@

\begin{abstract}
%\abstract{
%
The onset and bifurcation points of the $n$-cycles of
  a polynomial map are located
  through a characteristic equation
  connecting the cyclic polynomials of the cycle points.
The polynomials satisfied by the parameters
  of the logistic, H\'enon, and cubic maps
  at the onset and bifurcation points are obtained
  for $n$ up to 14, 9, and 9,
  respectively.
%
%}
\end{abstract}
\maketitle

@@

\begin{table*}[t]\footnotesize
  \caption{
  Characteristic polynomials $A_n\Rlam$ of
  the fixed points of $f^n$ of
  the simplified logistic map \refeq{logmaps}.
  }
\begin{center}
\begin{tabular}{lc}
\hline
  $n$
& $A_n(R, \; \lambda = 2^n X)
  \big\slash
   2^{n \NB(n)}$ $^\dagger$
\\
\hline
1
&
$X^2-X-R$
\\
2
&
  $
  \big[ \cancel{(R-X)^2 - X}\big]
  (R + X - 1)
  $
\\
3
&
$\begin{aligned}
\big[\cancel{
  X^2-(3R+1)X-R^3
}\big]
  \big[
  (X-1)^2
 + X R
 - R(R-1)^2
  \big]
\end{aligned}$
\\
4
&
$\begin{aligned}
\big[ \cancel{
  (R-1)^2 - X
} \big]
\big[ \cancel{
(R^2+X)^2 -(2R+1)^2 X
} \big]
\big[
  R^6-3 R^5+(X+3) (R^4 - R^3) -(X+2)(X-1) R^2 - (X-1)^3
\big]
\end{aligned}$
\\
5
&
\begin{minipage}{.97\linewidth}
\vspace*{2mm}
$\begin{aligned}
&\big[ \cancel{
  X^2-5 X (R^2+R)-X - R^5
  %R^5+5 X (R^2+R)-X^2+X
} \big]
\big[
-R^{15}+8 R^{14}-28 R^{13}+(X+60) R^{12}-(7 X+94) R^{11}
+(3 X^2 +20 X
\\
+&116) R^{10}
-(11 X^2+33 X+114) R^9
+2(3 X^2+20 X+47) R^8
-(2 X^3-20 X^2+37 X+69) R^7 \\
+&(3 X-11)(3X^2-3X+44) R^6
%-(3 X^4+17 X^3-53 X^2+7 X+26) R^5
-(X-1) (3 X^3+20 X^2-33 X-26) R^5
+(X-1)^2 (3 X^2+27 X+14) R^4 \\
+&(X-1)^3 (6 X+5) R^3
+(X-1)^4 (X+2) R^2+(X-1)^5 R+(X-1)^6
\big]
\end{aligned}$
\vspace{1mm}
\end{minipage}
\\
6
&
$\begin{aligned}
&\big[\cancel {
  (R-1)^3 + X
}\big]
\big[\cancel {
 (R^3 - X)^2 - (3R+1)^2 X
}\big]
\big[\cancel {
\big(R(R-1)^2-1-X\big)^2-(R-2)^2 X
}\big]
\big[
R^{27}-13 R^{26}+78 R^{25}\\
&+(X-293) R^{24}
+\dots
+(X-1)^6 (X^2+10 X+3) R^3
+(X-1)^7 (X+1) R^2-(X-1)^8 R+(X-1)^9
\big]
\end{aligned}$
\\
7
&
\begin{minipage}{.97\linewidth}
\vspace{1mm}
$\begin{aligned}
&\big[\cancel {
  -R^7 - 7 X R (R+1)^2 + X^2 - X
}\big]
\big[
-R^{63}+32 R^{62}-496 R^{61}
+4976 R^{60} + (X - 36440) R^{59}
- (30X
\\
-&208336) R^{58}
+\dots
+(X-1)^{15} (X^2+14 X+5) R^3
+2(X-1)^{16} (X+1) R^2
+(X-1)^{17} R
+(X-1)^{18}
\big]
\end{aligned}$
\end{minipage}
\\
\vdots & \vdots
\\
\hline
\multicolumn{2}{p{\textwidth}}{
$^\dagger$
$\NB(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$ [\refeq{necklace}]
is the number of the square-free cyclic polynomials.
%
The change of variable $\lambda \rightarrow X$ and
  the division by $2^{n \NB(n)}$ make the polynomials more compact.
%
The irrelevant factors from shorter cycles
(see \refsec{primfac}) are struck out.
The polynomials of $r$ for the original logistic map \refeq{logmap}
can be obtained by $R\rightarrow r(r-2)/4$.
} \\
\hline
\end{tabular}
\end{center}
\label{tab:Anlog}
\end{table*}

@@

\begin{table*}[t]\footnotesize
  \caption{
  Onset and bifurcation polynomials %$P_n(R, \pm1)$
  of the $n$-cycles of the simplified logistic map \refeq{logmaps}.}
\begin{center}
\begin{tabular}{lcc}
\hline
  $n$
& Onset $P_n(R, \; +1)$ $^{\dagger, \ddagger}$
& Bifurcation $P_n(R, \; -1)$ $^\dagger$
\\
\hline
1
&
$-\T-1$
&
$-\T+3$
\\
2
&
$-(\cancel{3-\T})$
&
$\T-5$
\\
3
&
$\begin{aligned}
-
\big( \cancel{
  \T^2-\T+7
}\big)
  (\T-7)
\end{aligned}$
&
$\begin{aligned}
 - \T^3 + 8\T^2 - 18\T + 81
\end{aligned}$
\\
4
&
$\begin{aligned}
\big( \cancel{
  \T - 5
} \big)
\big[ \cancel{
  (\T+1)^2 + 4
} \big]
\big[
  (\T-3)^3 - 108
\big]
\end{aligned}$

@@

\begin{minipage}{.48\linewidth}
%\vspace{3mm}
$\begin{aligned}
-
&\big( \cancel{
\T^4-\T^3+\T^2+9 \T+31
} \big)
\big(
\T^{11}-31 \T^{10} \\
+&416 \T^9 -3404 \T^8 +20548 \T^7-98258 \T^6 \\
+&370146 \T^5 -1171676 \T^4 +3301996 \T^3\\
-&7507332 \T^2+15699857 \T-28629151
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
&\big( \cancel{
\T^2-9 \T+21
} \big)
\big( \cancel{
\T^2+3 \T+3
} \big)
\big( \cancel{
\T^3-8\T^2} \\
+&\cancel{18\T-81
} \big)
\big(
\T^{20}-\dots+3063651608241
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
-
&\big( \cancel{
\T^6-\T^5+\T^4-\T^3
%\T^3(\T^2+1)(\T-1)
 +15T^2+97 \T+127
} \big) \\
&\big(
\T^{57}
-127\T^{56}
+\dots+
%581652040856250348581103942808504447
58165204\dots8504447
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\\
\vdots & \vdots & \vdots
\\
13
&

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
-&\big(\cancel{
\T^{12}-\T^{11}+\T^{10}
%-\T^9+\T^8-\T^7+\T^6+25 \T^5+703 \T^4+5121 \T^3+14847 \T^2
-\dots
+18433 \T+8191
}\big) \\
\big(
&\T^{4083}
 - 8191\T^{4082}
+ 33529856 \T^{4081}
- \dots \\
-&30826655683291995
\dots
27828275886475354111
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\begin{minipage}{.49\linewidth}
%\vspace{1mm}
$\begin{aligned}
-&\T^{4095} + 8192 \T^{4094} -33538048 \T^{4093} \\
+&\dots
-7361199006999 % 0439512081857
\dots
96207964555264\T
\\
+&29448390363448812
%0567620
\dots
%1182
352154556569141249
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\begin{table*}[t]\footnotesize
  \caption{
  Minimal polynomials $P_n(r, \lambda)$ of
  the $n$-cycles of the cubic map \refeq{cubic}.
  }
\begin{center}
\begin{tabular}{lc}
\hline
  $n$
& $P_n(r, \; \lambda)$ $^\dagger$
\\
\hline
1
&
$(\lambda - r) (\lambda + 2 r - 3)$
\\
2
&
  $
  \big[
  \cancel{\lambda - (2r+3)^2}
  \big]
  (\lambda + 2r^2 - 9)
  $
\\
3
&
$\begin{aligned}
  &\lambda^4
  + 2 (r+6)(r^2-9) \lambda^3
  -6 \big(8 r^6+12 r^5-66 r^4-81 r^3+54 r^2-243 r-729\big)
  \lambda^2
+2 (r^2-9) \big(16 r^7-252 r^5\\
-&216 r^4 +648 r^3+972 r^2+2187 r+4374\big) \lambda
+2 r (2r-3) (2 r+3)^2 (r^2-9) (2 r^2 - 9)^2 (4 r^2+9) + 531441
\end{aligned}$
\\
4
&
\begin{minipage}{.97\linewidth}
\vspace*{1mm}
$\begin{aligned}
&\big[ \cancel{
  (\lambda-8r^4+54r^2+81)^2
-4 (r^2-9)^2 \lambda
} \big]
\,^\ddagger\,
\big[
\lambda^8
+2(5 r^4-324) \lambda^7
+2(112 r^8-1296 r^6+3807 r^4-91854) \lambda^6 \\
+&\dots
+18075490334784 r^8
-61004779879896 r^6
-411782264189298 r^4
+1853020188851841
\big]
\end{aligned}$
\end{minipage}
\\
%5
%&
%\begin{minipage}{.97\linewidth}
%\vspace*{1mm}
%$\begin{aligned}
%\end{aligned}$
%\vspace{1mm}
%\end{minipage}
%\\
\vdots & \vdots
\\
\hline
\multicolumn{2}{p{\textwidth}}{
$^\dagger$
The factors from half-cycles (see \refsec{halfcycle}) are struck out.
}\\
\multicolumn{2}{p{\textwidth}}{
$^\ddagger$
The $n = 4$ half-cycles satisfy
$(\lambda^\odd + 9)^2 - 2(\lambda^\odd-27) r^2 - 8 r^4 = 0$,
  where $\lambda^\odd=\pm\sqrt\lambda$.
} \\
\hline
\end{tabular}
\end{center}
\label{tab:cubpolygen}
\end{table*}

\begin{table*}[t]\footnotesize
\caption{Onset and bifurcation polynomials of the $n$-cycles of the cubic map \refeq{cubic}.}
\begin{center}
\begin{tabular*}{\linewidth}{l c c}
%{c p{.2\linewidth} p{.35\linewidth} p{.35\linewidth}}
\hline
$n$
&
Onset $P_n(r, +1)$ $^\dagger$
&
Bifurcation $P_n(r, -1)$ $^\dagger$
\\
\hline
1
&
$-(r-1)^2$
&
$-(r+1)(r-2)$
\\
2
&
$-2 (r-2) (r+1) (r+2)^2$
&
$-(r^2-5) (2 r^2+6 r+5)$
\\
3
&
\begin{minipage}{.45\linewidth}
\vspace{3mm}
$\begin{aligned}
&(r^2+r+1) (4 r^2-14 r+13) \\
&(4 r^8+16 r^7-35 r^6-206 r^5-113 r^4\\
&+376 r^3+715 r^2+1690 r+2197)
\end{aligned}$
\vspace{1mm}
\end{minipage}
&
\begin{minipage}{.5\linewidth}
\vspace{3mm}
$\begin{aligned}
&16 r^{12}+24 r^{11}-288 r^{10}-434 r^9\\
+&1539 r^8+2358 r^7-1434 r^6-2556 r^5-8541 r^4\\
-&11816 r^3+15288 r^2+24696 r+38416
\end{aligned}$
\vspace{1mm}
\end{minipage}
\\
4
&
\begin{minipage}{.45\linewidth}
\vspace{3mm}
$\begin{aligned}
-&8(r^2-8) (r^2-5) (r^2+1) (2 r^2-6 r+5) \\
&(2 r^2+6 r+5) (2 r^4-13 r^2-25)^2 \\
&(1024 r^{22}-32512 r^{20}+402304 r^{18} \\
-&2364832 r^{16}+5389924 r^{14}+9715769 r^{12} \\
-&73067038 r^{10}+58934785 r^{8}+235761152 r^6 \\
-&160907264 r^4-671088640 r^2-2097152000)
\end{aligned}$
\vspace{3mm}
\end{minipage}
&
$\begin{aligned}
&-(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
&(8192 r^{32}-387072 r^{30}+7834624 r^{28} -88031232 r^{26}\\
&+585876512 r^{24}-2158227720 r^{22} +2211361312 r^{20}\\
&+15958823175 r^{18}  -68871388441 r^{16} +59290039854 r^{14}\\
&+234882618673 r^{12} -524807876277 r^{10} -72612143404 r^8\\
&+308406843576 r^6 +1539579145957 r^4-7984925229121)
\end{aligned}$
\\
\vdots & \vdots & \vdots
\\
8
&
$\begin{aligned}
&-8192 (r^4+1) (2 r^4-18 r^2+41) \\
&(8 r^4-48 r^3+108 r^2-108 r+41) \\
&(8 r^4+48 r^3+108 r^2+108 r+41) \dots\\
%&(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
%&(8192 r^{32}-\dots-7984925229121) \\
%&(16384 r^{36}-\dots-1310720000000000) \\
%&(131072 r^{40}-\dots-13422659310152401)^2 \\
&(22016722240\dots14954924752896r^{3108} \\
&-\dots-180097954\dots2522413056\times 10^{400})
\end{aligned}$
&
$\begin{aligned}
-&(17592186044416 r^{80} +\dots+ \\
&144564714832407908402064153121600801) \\
&(4841528421712030\dots03048551060078592 r^{3200}\\
&-\dots-25263420710\dots173884723232001)
\end{aligned}$
\\
\hline
\multicolumn{3}{p{\linewidth}}
{
$^\dagger$
Although $P_n(r, \lambda)$ is the minimal polynomial for a general $\lambda$,
it may contain a pre-factor (e.g., $-2$ in the $n=2, \lambda=+1$ case).
}\\
\hline
\end{tabular*}
\end{center}
\label{tab:cubpoly}
\end{table*}

>>>>

\documentclass[twocolumn]{revtex4-1}
%\usepackage[width=5.65in, height=9.3in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{centernot}
\usepackage{hyperref}
\usepackage{graphicx}
%\usepackage{times}
%\usepackage{setspace}
\usepackage{booktabs}
%\usepackage{appendix}

% strike-through style
%http://tex.stackexchange.com/questions/20609/strikeout-in-math-mode
%\usepackage{cancel} % strike out (cancel) in math mode
\usepackage{calc}
\newsavebox\CBox
\newcommand\hcancel[2][0.5pt]{%
  \ifmmode\sbox\CBox{$#2$}\else\sbox\CBox{#2}\fi%
  \makebox[0pt][l]{\usebox\CBox}%
  \rule[0.5\ht\CBox-#1/2]{\wd\CBox}{#1}}

@@

\begin{document}

@@

\begin{abstract}
%\abstract{
%
The onset and bifurcation points of $n$-cycles of
  several polynomial maps are located
  through a characteristic equation
  connecting cyclic polynomials of the cycle points.
The polynomials satisfied by the parameters
  of the logistic, H\'enon, and cubic maps
  at the onset and bifurcation points are obtained
  for $n$ up to 14, 9, and 9,
  respectively.
%
%}
\end{abstract}
\maketitle

@@

\begin{table*}[t]\footnotesize
  \caption{
  Characteristic polynomials $A_n\Rlam$ of
  the fixed points of $f^n$ of
  the simplified logistic map \refeq{logmaps}.
  }
\begin{center}
\begin{tabular}{lc}
\hline
  $n$
& $A_n(R, \; \lambda = 2^n X)
  \big\slash
   2^{n \NB(n)}$ $^\dagger$
\\
\hline
1
&
$X^2-X-R$
\\
2
&
  $
  \hcancel{
    \big[ (R-X)^2 - X \big]
  }
  (R + X - 1)
  $
\\
3
&
$\begin{aligned}
  \hcancel{
    \big[ X^2-(3R+1)X-R^3 \big]
  }
  \big[
  (X-1)^2
 + X R
 - R(R-1)^2
  \big]
\end{aligned}$
\\
4
&
$\begin{aligned}
  \hcancel{
    \big[ (R-1)^2 - X \big]
  }
  \hcancel{
    \big[ (R^2+X)^2 -(2R+1)^2 X \big]
  }
\big[
  R^6-3 R^5+(X+3) (R^4 - R^3) -(X+2)(X-1) R^2 - (X-1)^3
\big]
\end{aligned}$
\\
5
&
\begin{minipage}{.97\linewidth}
\vspace*{2mm}
$\begin{aligned}
&
  \hcancel{
    \big[ X^2-5 X (R^2+R)-X - R^5 \big]
    %R^5+5 X (R^2+R)-X^2+X
  }
\big[
-R^{15}+8 R^{14}-28 R^{13}+(X+60) R^{12}-(7 X+94) R^{11}
+(3 X^2 +20 X
\\
+&116) R^{10}
-(11 X^2+33 X+114) R^9
+2(3 X^2+20 X+47) R^8
-(2 X^3-20 X^2+37 X+69) R^7 \\
+&(3 X-11)(3X^2-3X+44) R^6
%-(3 X^4+17 X^3-53 X^2+7 X+26) R^5
-(X-1) (3 X^3+20 X^2-33 X-26) R^5
+(X-1)^2 (3 X^2+27 X+14) R^4 \\
+&(X-1)^3 (6 X+5) R^3
+(X-1)^4 (X+2) R^2+(X-1)^5 R+(X-1)^6
\big]
\end{aligned}$
\vspace{1mm}
\end{minipage}
\\
6
&
$\begin{aligned}
&
  \hcancel {
    \big[ (R-1)^3 + X \big]
    \big[ (R^3 - X)^2 - (3R+1)^2 X \big]
    \big[ \big(R(R-1)^2-1-X\big)^2-(R-2)^2 X \big]
  }
\big[
R^{27}-13 R^{26}+78 R^{25}\\
&+(X-293) R^{24}
+\dots
+(X-1)^6 (X^2+10 X+3) R^3
+(X-1)^7 (X+1) R^2-(X-1)^8 R+(X-1)^9
\big]
\end{aligned}$
\\
7
&
\begin{minipage}{.97\linewidth}
\vspace{1mm}
$\begin{aligned}
&
  \hcancel {
    \big[ -R^7 - 7 X R (R+1)^2 + X^2 - X \big]
  }
\big[
-R^{63}+32 R^{62}-496 R^{61}
+4976 R^{60} + (X - 36440) R^{59}
- (30X
\\
-&208336) R^{58}
+\dots
+(X-1)^{15} (X^2+14 X+5) R^3
+2(X-1)^{16} (X+1) R^2
+(X-1)^{17} R
+(X-1)^{18}
\big]
\end{aligned}$
\end{minipage}
\\
\vdots & \vdots
\\
\hline
\multicolumn{2}{p{\textwidth}}{
$^\dagger$
$\NB(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$ [\refeq{necklace}]
is the number of the simple square-free cyclic polynomials.
%
The change of variable $\lambda \rightarrow 2^n X$ and
  the division by $2^{n \NB(n)}$ make the polynomials more compact.
%
The irrelevant factors from shorter cycles
(see \refsec{primfac}) are struck out.
The polynomials of $r$ for the original logistic map \refeq{logmap}
can be obtained by $R\rightarrow r(r-2)/4$.
} \\
\hline
\end{tabular}
\end{center}
\label{tab:Anlog}
\end{table*}

@@

\begin{table*}[t]\footnotesize
  \caption{
  Onset and bifurcation polynomials %$P_n(R, \pm1)$
  of the $n$-cycles of the simplified logistic map \refeq{logmaps}.}
\begin{center}
\begin{tabular}{lcc}
\hline
  $n$
& Onset $P_n(R, \; +1)$ $^{\dagger, \ddagger}$
& Bifurcation $P_n(R, \; -1)$ $^\dagger$
\\
\hline
1
&
$-\T-1$
&
$-\T+3$
\\
2
&
$-\hcancel{ (3 - \T) }$
&
$\T-5$
\\
3
&
$\begin{aligned}
-
\hcancel{
  ( \T^2 - \T + 7 )
}
  (\T-7)
\end{aligned}$
&
$\begin{aligned}
 (- \T^3 + 8\T^2 - 18\T + 81 )
\end{aligned}$
\\
4
&
$\begin{aligned}
\hcancel{
  (\T - 5)
  \big[ (\T+1)^2 + 4 \big]
}
\big[
  (\T-3)^3 - 108
\big]
\end{aligned}$

@@

\begin{minipage}{.48\linewidth}
%\vspace{3mm}
$\begin{aligned}
-
&
\hcancel{
  ( \T^4-\T^3+\T^2+9 \T+31 )
}
\big(
\T^{11}-31 \T^{10} \\
+&416 \T^9 -3404 \T^8 +20548 \T^7-98258 \T^6 \\
+&370146 \T^5 -1171676 \T^4 +3301996 \T^3\\
-&7507332 \T^2+15699857 \T-28629151
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
&
\hcancel{
  (\T^2-9 \T+21)
  (\T^2+3 \T+3)
  (\T^3-8\T^2} \\
&
  \hcancel{ +18\T-81 ) }
\big(
\T^{20}-\dots+3063651608241
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
-
&
\hcancel{
  (\T^6-\T^5+\T^4-\T^3
%\T^3(\T^2+1)(\T-1)
 +15T^2+97 \T+127)
} \\
&\big(
\T^{57}
-127\T^{56}
+\dots+
%581652040856250348581103942808504447
58165204\dots8504447
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\\
\vdots & \vdots & \vdots
\\

%13
%&
%
%\begin{minipage}{.48\linewidth}
%%\vspace{1mm}
%$\begin{aligned}
%-&
%  \hcancel{
%  \big(
%    \T^{12}-\T^{11}+\T^{10}
%    %-\T^9+\T^8-\T^7+\T^6+25 \T^5+703 \T^4+5121 \T^3+14847 \T^2
%    -\dots
%    +18433 \T+8191
%  \big)
%} \\
%\big(
%&\T^{4083}
% - 8191\T^{4082}
%+ 33529856 \T^{4081}
%- \dots \\
%-&30826655683291995
%\dots
%27828275886475354111
%\big)
%\end{aligned}$
%%\vspace{2mm}
%\end{minipage}
%
%&
%\begin{minipage}{.49\linewidth}
%%\vspace{1mm}
%$\begin{aligned}
%-&\T^{4095} + 8192 \T^{4094} -33538048 \T^{4093} \\
%+&\dots
%-7361199006999 % 0439512081857
%\dots
%96207964555264\T
%\\
%+&29448390363448812
%%0567620
%\dots
%%1182
%352154556569141249
%\end{aligned}$
%\vspace{2mm}
\\
14
&

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
&
\hcancel{
  \big(
    \T^6 + 3 \T^5 + 9 \T^4 + 27 \T^3 + 67\T^2 + 89 \T + 43
  \big)
} \\
&\hcancel{
  \big(
    \T^6 - 25 \T^5 + 261 \T^4 -1457 \T^3 + 4589 \T^2 - 7737 \T +5461
  \big)
} \\
&\hcancel{
  \big(
    -\T^{63} + 128 \T^{62} - \dots
    + 978621573341\dots3892330031361
    %+ 97862157334118736160267353892330031361
  \big)
} \\
\big(
&\T^{8052}
- 16102\T^{8051}
+ 129605001\T^{8050}
- \dots \\
+&354338440786337482
\dots
91101574588267047561
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

@@

\begin{minipage}{.49\linewidth}
%\vspace{1mm}
$\begin{aligned}
-&\T^{8127} + 16252 \T^{8126} - 132031248 \T^{8125} \\
+&\dots
+234550833883692
\dots
06625000000000000\T
\\
+&
93826059892194743
\dots
18759918212890625
\end{aligned}$

\end{minipage}

@@

\begin{table*}[t]\footnotesize
  \caption{
  Minimal polynomials $P_n(r, \lambda)$ of
  the $n$-cycles of the cubic map \refeq{cubic}.
  }
\begin{center}
\begin{tabular}{lc}
\hline
  $n$
& $P_n(r, \; \lambda)$ $^\dagger$
\\
\hline
1
&
$(\lambda - r) (\lambda + 2 r - 3)$
\\
2
&
  $
  \hcancel{ [\lambda - (2r+3)^2 ] }
  (\lambda + 2r^2 - 9)
  $
\\
3
&
$\begin{aligned}
  &\lambda^4
  + 2 (r+6)(r^2-9) \lambda^3
  -6 \big(8 r^6+12 r^5-66 r^4-81 r^3+54 r^2-243 r-729\big)
  \lambda^2
+2 (r^2-9) \big(16 r^7-252 r^5\\
-&216 r^4 +648 r^3+972 r^2+2187 r+4374\big) \lambda
+2 r (2r-3) (2 r+3)^2 (r^2-9) (2 r^2 - 9)^2 (4 r^2+9) + 531441
\end{aligned}$
\\
4
&
\begin{minipage}{.97\linewidth}
\vspace*{1mm}
$\begin{aligned}
&
\hcancel{
  \big[
    (\lambda-8r^4+54r^2+81)^2
    -4 (r^2-9)^2 \lambda
  \big]
}
\,^\ddagger\,
\big[
\lambda^8
+2(5 r^4-324) \lambda^7
+2(112 r^8-1296 r^6+3807 r^4-91854) \lambda^6 \\
+&\dots
+18075490334784 r^8
-61004779879896 r^6
-411782264189298 r^4
+1853020188851841
\big]
\end{aligned}$
\end{minipage}
\\
%5
%&
%\begin{minipage}{.97\linewidth}
%\vspace*{1mm}
%$\begin{aligned}
%\end{aligned}$
%\vspace{1mm}
%\end{minipage}
%\\
\vdots & \vdots
\\
\hline
\multicolumn{2}{p{\textwidth}}{
$^\dagger$
The factors from half-cycles (see \refsec{halfcycle}) are struck out.
}\\
\multicolumn{2}{p{\textwidth}}{
$^\ddagger$
The $n = 4$ half-cycles satisfy
$(\lambda^\odd + 9)^2 - 2(\lambda^\odd-27) r^2 - 8 r^4 = 0$,
  where $\lambda^\odd=\pm\sqrt\lambda$.
} \\
\hline
\end{tabular}
\end{center}
\label{tab:cubpolygen}
\end{table*}

\begin{table*}[t]\footnotesize
\caption{Onset and bifurcation polynomials of the $n$-cycles of the cubic map \refeq{cubic}.}
\begin{center}
\begin{tabular*}{\linewidth}{l c c}
%{c p{.2\linewidth} p{.35\linewidth} p{.35\linewidth}}
\hline
$n$
&
Onset $P_n(r, +1)$ $^\dagger$
&
Bifurcation $P_n(r, -1)$ $^\dagger$
\\
\hline
1
&
$-(r-1)^2$
&
$-(r+1)(r-2)$
\\
2
&
$-2 (r-2) (r+1) (r+2)^2$
&
$-(r^2-5) (2 r^2+6 r+5)$
\\
3
&
\begin{minipage}{.45\linewidth}
\vspace{3mm}
$\begin{aligned}
&(r^2+r+1) (4 r^2-14 r+13) \\
&(4 r^8+16 r^7-35 r^6-206 r^5-113 r^4\\
&+376 r^3+715 r^2+1690 r+2197)
\end{aligned}$
\vspace{1mm}
\end{minipage}
&
\begin{minipage}{.5\linewidth}
\vspace{3mm}
$\begin{aligned}
&16 r^{12}+24 r^{11}-288 r^{10}-434 r^9\\
+&1539 r^8+2358 r^7-1434 r^6-2556 r^5-8541 r^4\\
-&11816 r^3+15288 r^2+24696 r+38416
\end{aligned}$
\vspace{1mm}
\end{minipage}
\\
4
&
\begin{minipage}{.45\linewidth}
\vspace{3mm}
$\begin{aligned}
-&8(r^2-8) (r^2-5) (r^2+1) (2 r^2-6 r+5) \\
&(2 r^2+6 r+5) (2 r^4-13 r^2-25)^2 \\
&(1024 r^{22}-32512 r^{20}+402304 r^{18} \\
-&2364832 r^{16}+5389924 r^{14}+9715769 r^{12} \\
-&73067038 r^{10}+58934785 r^{8}+235761152 r^6 \\
-&160907264 r^4-671088640 r^2-2097152000)
\end{aligned}$
\vspace{3mm}
\end{minipage}
&
$\begin{aligned}
&-(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
&(8192 r^{32}-387072 r^{30}+7834624 r^{28} -88031232 r^{26}\\
&+585876512 r^{24}-2158227720 r^{22} +2211361312 r^{20}\\
&+15958823175 r^{18}  -68871388441 r^{16} +59290039854 r^{14}\\
&+234882618673 r^{12} -524807876277 r^{10} -72612143404 r^8\\
&+308406843576 r^6 +1539579145957 r^4-7984925229121)
\end{aligned}$
\\
\vdots & \vdots & \vdots
\\
%8
%&
%$\begin{aligned}
%&-8192 (r^4+1) (2 r^4-18 r^2+41) \\
%&(8 r^4-48 r^3+108 r^2-108 r+41) \\
%&(8 r^4+48 r^3+108 r^2+108 r+41) \dots\\
%%&(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
%%&(8192 r^{32}-\dots-7984925229121) \\
%%&(16384 r^{36}-\dots-1310720000000000) \\
%%&(131072 r^{40}-\dots-13422659310152401)^2 \\
%&(22016722240\dots14954924752896r^{3108} \\
%&-\dots-180097954\dots2522413056\times 10^{400})
%\end{aligned}$
%&
%$\begin{aligned}
%-&(17592186044416 r^{80} +\dots+ \\
%&144564714832407908402064153121600801) \\
%&(4841528421712030\dots03048551060078592 r^{3200}\\
%&-\dots-25263420710\dots173884723232001)
%\end{aligned}$
%\\
9
&
$\begin{aligned}
&(r^6 + r^3 + 1)
(64 r^6 - 576 r^5 + 2160 r^4 - 4328 r^3 + 4896 r^2 \\
&- 2970 r + 757)
(65536 r^{24} + 196608 r^{23} - \dots + 328385156401) \cdots\\
&(100257396069318593562485\dots27041918452769115602944 r^{9792} \\
&+\dots+100777071891533412274\dots669779415034840760335533)
\end{aligned}$
&
$\begin{aligned}
&4205099973631272542535\dots26734123312649890430976 r^{9828} \\
&-619915838112722198220\dots14445875084684733448192 r^{9826} \\
&+\dots+186361973456670282\dots45890460766629265408 r^{3} \\
&+279917391437103331960\dots789652523552928732020736
\end{aligned}$
\\
%
%
%
\hline
%
%
%
\multicolumn{3}{p{\linewidth}}
{
$^\dagger$
Although $P_n(r, \lambda)$ is the minimal polynomial for a general $\lambda$,
it may contain a pre-factor (e.g., $-2$ in the $n=2, \lambda=+1$ case).
}\\
\hline
\end{tabular*}
\end{center}
\label{tab:cubpoly}
\end{table*}

\begin{table}[h]\footnotesize
\caption{
  Smallest positive $r$ at the onset and bifurcation points
  of the $n$-cycles of the cubic map.
  }
\begin{center}
%\begin{tabular}{l l l l}
\begin{tabularx}{\linewidth}{
  >{\hsize=0.5\hsize\raggedright\arraybackslash}X
  >{\hsize=1.6\hsize}X
  >{\hsize=1.6\hsize}X
  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
}
%\begin{tabular*}{\textwidth}{l l l l c | c l l l l}
\hline
  $n^\dagger$
& Onset$^\ddagger$
& Bifurcation$^\ddagger$
& \#$^*$ \\
\hline
$1$     & $1.0000000000_1$      &  $2.0000000000_1$       & 2   \\
$2'$    & $2.0000000000_1$      &  $2.2360679775_2$       & 2   \\
$3$     & $2.4504409645_{8}$    &  $2.4608286739_{12}$    & 4   \\
$4$     & $2.5478350393_{22}$   &  $2.5488312193_{32}$    & 8   \\
$4''$   & $2.2360679775_{2}$    &  $2.2880317545_{32}$    & 2   \\
$5$     & $2.3939250274_{112}$  &  $2.3957922744_{120}$   & 24  \\
$6$     & $2.3334877526_{304}$  &  $2.3355337580_{336}$   & 56  \\
$6'$    & $2.4608286739_{12}$   &  $2.4657090579_{336}$   & 4   \\
$7$     & $2.3729872678_{1080}$ &  $2.3732727868_{1092}$  & 156 \\
$8$     & $2.3525990555_{3108}$ &  $2.3527637793_{3200}$  & 400 \\
$8'$    & $2.5488312193_{32}$   &  $2.5493247379_{3200}$  & 8   \\
$8'''$  & $2.2880317545_{32}$   &  $2.2992279397_{3200}$  & 2   \\
$9$     & $2.3651805877_{9792}$ &  $2.3652188703_{9828}$  & 1092 \\
\hline
\multicolumn{4}{p{\linewidth}}{
$^\dagger$
  $\,'$, $\,''$, or $\,'''$ means that the cycle is undergoing
    the first, second, or third successive period-doubling, respectively.
} \\
\multicolumn{4}{p{\linewidth}}{
$^\ddagger$
  The subscripts are the degrees of the corresponding minimal polynomial.
} \\
\multicolumn{4}{p{\linewidth}}{
$^*$
  The number of similar cycles
    (for $n > 1$, only half of them have positive $r$).
} \\
\hline
%\end{tabular}
\end{tabularx}
%\end{tabular*}
\end{center}
\label{tab:crval}
\end{table}
